Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2020-12-24 journalMS/article.tex
updated journal article

Using Monte Carlo simulation, Fasano and Franceschini approximated the distribution of D for significance testing -- as a function of $D$, the sample size $N$, and the coefficient of correlation $r$.

@@

In their paper, Fasano and Franceschini use Monte Carlo simulation to approximate the distribution of D as a function of $D$, the sample size $N$, and the coefficient of correlation $r$. The resultant distributional approximation -- as described above in equation \ref{eq:4} -- can be used to test the significance levels for the two-dimensional K-S test.

Note that the above formulas are accurate enough when $N \geq 20$, and when the indicated probability (significance level) is less than (more significant than) 0.20 or so. When the indicated probability is $> 0.20$, its value may not be accurate, but the implication that the data and model (or two data sets) are not significantly different is certainly correct.

>>>>

Using Monte Carlo simulation, Fasano and Franceschini created a series of critical value look up tables of values of D -- as a function of $D$, the sample size $N$, and the coefficient of correlation $r$. Teukolsky and Press later defined an approximate fit to this data in equation \ref{eq:4} for quick computaion \cite{numericalRecipes}.

@@

In their paper, Fasano and Franceschini use Monte Carlo simulation to approximate the distribution of D as a function of $D$, the sample size $N$, and the coefficient of correlation $r$. The resultant distributional approximation fit by Teukolsky and Press-- as described above in equation \ref{eq:4} -- can be used to test the significance levels for the two-dimensional K-S test.

Note that the above formulas are accurate when $N \geq 20$, and when the indicated probability (significance level) is less than (more significant than) $\sim 0.20$. When the indicated probability is $> 0.20$, its value may not be accurate, but the implication that the two data sets are not significantly different is certainly correct.
